### 2020-12-23 paper/localpsf.tex
wrote about hessian product convolutions in existing work. made more edits to Section 2

A product-convolution type approximation of the Hessian in a seismic imaging problem was used in [CITE GEORG].

@@

Demanet matrix probing can be interpreted as convolution-product.

@@

Geometry-aware weighting functions vs radial basis functions. Kriging.

@@

\section{Constructing the approximation}
\label{sec:method}
This section describes how we compute the convolution kernels, $\varphi_i$, and weighting functions, $w_i$, for the product-convolution approximation, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, given by
\begin{equation}
\left(\widetilde{\mathcal{A}}u\right)(v) := \left( v,~ \sum_{i=1}^r \varphi_i \ast \left(w_i \cdot u\right) \right)_{L^2(\Omega)}.
\end{equation}

We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). We use a greedy algorithm to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). Ensuring that the points $x_i$ are well separated from each other requires estimating the supports of the functions $\langle\mathcal{A},\delta_{x}\rangle^*$ (Section \ref{eq:mean_and_covariance_estimation}).

>>>>

Product-convolution type approximations of Hessians have been used in a seismic inverse problem in [CITE GEORG], and in an advection-diffusion inverse problem in [CITE MY PAPER]. In [DEMANET SEISMIC], matrix probing [DEMANET MATRIX] is used to approximate the Hessian in a seismic inverse problem as the sum of simple pseudodifferential operators. Although it is not explicitly mentioned, the approximation in [DEMANET SEISMIC] could be interpreted as a convolution-product interpolation, which is like a product-convolution approximation, except the order of pointwise multiplications and convolutions is reversed in \eqref{eq:product_convolution}.

@@

%Demanet matrix probing can be interpreted as convolution-product.

@@

%Geometry-aware weighting functions vs radial basis functions. Kriging.

@@

\section{Constructing the approximation}
\label{sec:method}
This section describes how we compute the convolution kernels, $\varphi_i$, and weighting functions, $w_i$, for the product-convolution approximation, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, given in \eqref{eq:product_convolution}.
\begin{itemize}
\item We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). 
\item We use a greedy algorithm to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). 
\item Ensuring that the points $x_i$ are well separated from each other requires a-priori estimates of the supports of the functions $\langle\mathcal{A},\delta_{x}\rangle^*$ (Section \ref{eq:mean_and_covariance_estimation}). 
\item The weighting functions are defined as the smoothest functions (in a least-squares sense) that interpolate the points $x_i$; constructing the weighting functions requires solving two Poisson PDEs per point $x_i$ (Section \ref{sec:weighting_functions}).
\end{itemize}
The complete algorithm for constructing $\widetilde{\mathcal{A}}$ is shown in Algorithm \ref{alg:construct_Atilde}.

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		Compute spatially varying mean, $\mu$, and covariance, $\Sigma$, using Algorithm \ref{alg:varhpi_mean_cov}.

		\For{$b=1,2,\dots,\text{max\_batches}$}{
			Choose a batch of sample points, $S_b$, using Algorithm \ref{alg:point_choice}

			Compute $\eta^b$ by applying $\mathcal{A}$ to the dirac comb associated with $S_b$ (Section \ref{sec:get_impulse_response})

			Compute weighting functions $w_i$ using Algorithm \ref{alg:weighting_functions_incremental}. In lines 2 and 3 of Algorithm \ref{alg:weighting_functions_incremental}, only solve for $\psi_i$ and $\theta_i$ associated with new points $x_i$ in $S_b$. The functions $\psi_i$ and $\theta_i$ associated with points in previous batches have already been computed in previous iterations of this for loop.
		}

		%		\Return{$\mu$, $\Sigma$}
	}
	\caption{Construct product-convolution approximation $\widetilde{\mathcal{A}}$}
	\label{alg:construct_Atilde}
\end{algorithm2e}
